---
title: "Final Assignment"
output: html_notebook
---


```{r}
#load data & data summary
setwd("C:\\Users\\37676\\Desktop\\JHU Data Science\\Practical Machine Learning")
data <- read.csv("pml-training.csv",header=TRUE)
predict_data <- read.csv("pml-testing.csv",header=TRUE)
```

```{r}
str(data)
```


```{r}
#Remove columns in which N/A is more than 10%
library(dplyr)
data <- data %>% select_if(function(x) sum(is.na(x))/nrow(data) < 0.1)

```

```{r}
# check the dataset
str(data)
```

```{r}
# some of the columns contains a lot of blanks, also we would like to keep only columns of interest, ID and timestamp will be removed
y <- data$classe
data <- data %>% select_if(function(x) is.numeric(x))
data$class <- y
data<-data[,c(4:57)]
```


```{r}
#Predicted dataset cleaning
library(dplyr)
predict_data <- predict_data %>% select_if(function(x) sum(is.na(x))/nrow(predict_data) < 0.1)
predict_data <- predict_data %>% select_if(function(x) is.numeric(x))
pred_ID <-predict_data$X
predict_data<-predict_data[,c(4:57)]
```

```{r}
# split dataset into training set and testing set
library(ggplot2)
library(lattice)
library(nnet)
library(caret)
library(e1071)
#Stratfied sampling
set.seed(787)
TrainingDataIndex <- createDataPartition(data$class, p=0.75, list = FALSE)
#create training set and testing set
training <- data[TrainingDataIndex,]
testing <- data[-TrainingDataIndex,]
TrainingParameters <- trainControl(method = "repeatedcv", number = 10, repeats=10)
```

```{r}
#Train KNN model
KNNModel <- train(training[,-54], training$class,
                  method = "knn",
                  trControl = trainControl(method = "boot"),
                  preProcess=c("scale","center"))
```

```{r}
#Testing with KNN
KNNPredictions <- predict(KNNModel, testing)
# Create confusion matrix
cmKNN <- confusionMatrix(KNNPredictions, testing$class)
print(cmKNN)
```

```{r}
# Predict the result with KNN
KNN_Pred <- predict(KNNModel, predict_data)
predict_result<-cbind.data.frame(pred_ID,KNN_Pred)
predict_result
```

Train the dataset with neutral network
```{r}
NNModel <- train(training[,-57], training$class,
                  method = "nnet",
                  preProcess=c("scale","center"),
                  na.action = na.omit)
```

```{r}
```
Data Resource: Ugulino, W.; Cardador, D.; Vega, K.; Velloso, E.; Milidiu, R.; Fuks, H. Wearable Computing: Accelerometers' Data Classification of Body Postures and Movements. Proceedings of 21st Brazilian Symposium on Artificial Intelligence. Advances in Artificial Intelligence - SBIA 2012. In: Lecture Notes in Computer Science. , pp. 52-61. Curitiba, PR: Springer Berlin / Heidelberg, 2012. ISBN 978-3-642-34458-9. DOI: 10.1007/978-3-642-34459-6_6.

```{r}
